```{r setup, include = FALSE}
source("analysis.R")
```

# **Mass Shooting Report for 2018**

## _Summary Information_

During the year of 2018, there were many occurrences of mass shootings happening all around the US states. Approximately `r total_shootings` shootings occurred and many lives were either lost or injured. To be more exact, it was recorded that `r total_lives_lost` lives were lost and `r total_injured` were injured due to the mass shootings during 2018. The city that was most impacted by the shootings was `r city_impacted`. `r city_impacted` had been a victim of `r chicago_num` different shootings during 2018 and that is a real shame. However, state-wise there were two different states that had the same amount of shootings that occurred during 2018: `r state_most_impacted1` and `r state_most_impacted2`. They had a total of `r num_impacted` shootings within their states. Of the whole 2018, there were two dates that had the same amount of people who were either killed or injured during the shootings: `r most_shooting_day1` and `r most_shooting_day2`. On both these days, the total number of people who were either killed or injured totaled to `r most_shooting`. 

## _Summary Table_
```{r echo = FALSE}
library(knitr)
kable(summary_table, caption = "This table shows each state and their total amount of shootings that occurred within them. Plus, the total amount of people who were either killed or injured within their designated state during the year of 2018")
```


## _Chicago Shooting of 2018_
[Source](https://www.cnn.com/2018/08/05/us/chicago-weekend-shootings/index.html)

One of the biggest shootings that happened in Chicago during 2018 occurred during the weekend of Friday, August 3rd and Sunday, August 5th. There was not just one shooting, but multiple, and that lead to the death of 12 people and 66 injured. The biggest shooting that happened during that weekend was at a street party where a lot of people were in close contact with one another. Sadly, majority of the people who were killed were children, ranging from age 13 and up. Police officers understands the situation of what is going on in Chicago, but even with the decrease of murder and shootings happening at this time, there's always going to be a situation that they can't prevent. 
This event corresponds with the information I shared above. Looking at the city with the most amount of shootings, `r city_impacted`, you can see that this shooting event was the main reason why there was a huge increase in their total injured, which is totaled to `r chicago_total_injured`. With this huge spike in people getting injured, that's why they are the city who is most affected by the shootings.


## _Interactive Map_
This map is to illustrate where all the shootings have occurred during the year of 2018. In this map, the blue circle represents the number of people who were injured in a shooting, and the red circle represents the number of people who were killed in a shooting. The darker the circles are, the more shootings there was in that general area. The size of the circle represents the amount of people who were either killed or injured. The bigger the circle, the more people killed or injured during the shooting. 

This map is used to help show where majority of the shootings occurred in the United States. Additionally, my map helps show where the shooting with the most cause of death or injury occurs as well. For example, you can see that there is a huge blue circle in Philadelphia. This huge circle represents a shooting that caused 19 injuries towards people. This map helps distinguish which shooting caused the most death and most injuries between states.
`r map_US`
An interesting thing I noticed from my map is that majority of the shootings occurred in the eastern part of the United states. Splitting the US in half, you can see that a lot of states and cities on the right side of the map are being experiencing many shootouts compared to the left side.

Another interesting thing I noticed from my map is that there are very few to no shootings occurring in the upper most part of the United States. You can see that there were no shootings in Montana, North Dakota, South Dakota, and Wyoming. I'm surprised that there weren't any shootings recorded, but again that's really good to hear.


## _State Most Impacted By Shootings_
```{r, echo=FALSE}
most_state_shooting
```

This bar chart helps distinguish the amount of shootings occurring in different states. This is a really good choice of chart to display this information because you can instantly tell which bar has the most and which has the least. Plus, the color helps to see which bar is more because the lighter the bar, the more shootings have occurred in the state. With this chart, you can instantly tell that the two states most affected by the shootings were `r state_most_impacted1` and `r state_most_impacted2`. 

An interesting thing I noticed was that the states less impacted by the shootings were Utah, Massachusetts, and Delaware. Kind of makes sense too because we rarely hear any news in relation to those states. Another interesting thing I noticed about this is that the top three states impacted by shootings are the states that we hear the most of on the news.